\documentclass[a4paper]{article}
\usepackage{verbatim}
\begin{comment}
Why hello there! I see you've chosen the red pill!
Welcome to one of the more painful yet rewarding ways to write a resume!
Hope you enjoy the mess below! -Alex
\end{comment}
\usepackage{array}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{anysize}
\usepackage{tabularx}
\usepackage{caption}
\usepackage{longtable}
\usepackage{multicol}
\marginsize{3.5cm}{3.5cm}{1cm}{1cm}

\addtolength{\oddsidemargin}{-.825in}
\addtolength{\evensidemargin}{-.825in}

\addtolength{\textwidth}{1.75in}
\setlist[itemize]{leftmargin=*}

\begin{document}
    \pagenumbering{gobble}
    \begin{multicols}{2}
        \begin{LARGE}
        \noindent
        Alexander Laties\\
        \end{LARGE}
        \fbox{\parbox{0.35 \textwidth}{
        245 Manhattan Avenue\\
        Apt 5B\\
        Brooklyn, NY 11211\\
        Phone: 267 825 2530\\
        Website: http://alex.laties.info/ \\
        E-Mail: alex@laties.info \\
        Github: https://github.com/alex-laties
        }}
        \columnbreak

        \begin{Large}
        \noindent
        Education\\
        \end{Large}
        \begingroup
        \fontsize{8pt}{12pt}\selectfont
        \noindent
        Fall 2007 - Spring 2010 \\
        University of Pennsylvania School of Engineering \\
        Majored in Computer Science.
        \begin{itemize}
            \item Learned some theory 
            \item Implemented a CPU, an OS shell, and some sweet buffer overflows 
            \item Dropped out due to health reasons.
        \end{itemize}
        \endgroup
    \end{multicols}
    

    \begin{Large}
        \noindent
        General Purpose Software Developer \\
    \end{Large}

    \begingroup
        \fontsize{8pt}{12pt}\selectfont
        \noindent
        I'm general purpose programmer who has worked on building, maintaining, and scaling services. I have no strong language preference. I have reasonable experience with Ruby, Python, and Golang. I have experience with larger IDEs, such as Visual Studio, MonoDevelop, and XCode, but claim no great proficiencies. \\
        \par
        \noindent
        I have worked with teams in an agile style to quickly deliver features and products. I have worked with ticketing systems, such as Jira and Trello, to manage work loads. I have worked with source control systems, like Subversion and Git. I have experience with Test Driven Development through the use of unit tests. \\
        \par
        \noindent
        I have contributed some code to open source projects like Bottlepy, watchwithme, and pyrollbar.\\
        \par
        \noindent
        I like attempting to automate my home in my free time.\\
    \endgroup

    \begin{Large}
        \noindent
        Work History
    \end{Large}
    \begingroup
        \fontsize{8pt}{12pt}\selectfont

        \begin{multicols}{3}
            \noindent
            January 2016 - February 2017 \\
            Uber Technologies, LLC. \\
            Network Engineer \\
            \begin{itemize}
                \item Worked for the UberATG effort.
                \item Implemented and maintained an IPAM system with Collins and phpIPAM.
                \item Implemented and maintained a metrics and alerting system for network devices and services using Prometheus and alertmanager.
                \item Implemented and maintained a serial port based initial configuration system for Juniper switches with golang.
                \item Triaged, diagnosed, and solved mission critical flaws in systems, networks, and deployments.
            \end{itemize}
            \columnbreak
            April 2014 - December 2015 \\
            Tumblr, Inc \\
            Site Reliability Engineer \\
            \begin{itemize}
                \item Worked with Ruby and Puppet to maintain internal services.
                \item Maintained an HTTP loadbalancing layer implemented with haproxy and nginx.
                \item Maintained an HTTP caching layer implemented with varnish.
                \item Improved availability of services through anycast with OSPF + bird and quagga.
                \item Stress tested the HTTP loadbalancing layer with load generators vegeta, siege, apib, slowloris.pl, and hping3.
                \item Improved in-memory credential management across Ruby, Python, and PHP services with a C++ library and wrappers.
            \end{itemize}
            \columnbreak
            March 2012 - October 2013 \\
            Voxy, Inc \\
            Software Engineer 
            \begin{itemize}
                \item Worked with Django on Python 2.7 to maintain a web application and mobile API.
                \item Built prototypes for internal CRMs.
                \item Built a new mobile API stack in Bottle.
                \item Set up loadbalancing for web and mobile stacks using haproxy and pacemaker.
                \item Set up and wrote initial recipes for Chef provisioning service.
                \item Also dealt with PostgreSQL, MongoDB, Varnish, Celery, Redis, uwsgi, gunicorn, and nginx. 
            \end{itemize}
        \end{multicols}
    \endgroup
\end{document}
